---
title:
name: "Adeyinka"
surname: "Falaye" 
position: "Computer/Data Analytics Scientist"
address: "Unit 45/21-25 Seven Hills, Baulkham Hills NSW 2153"
phone: +61 4040 63256
www: .com
email: "falayeadeyinka@outlook.com"
twitter: falaye
github: falaye-sydney
linkedin: falaye
date: "`r format(Sys.time(), '%B %Y')`"
output: 
    #vitae::awesomecv
    vitae::markdowncv:
         theme: kjhealy
    #vitae::latexcv:
        #theme: classic
    #vitae::hyndman
    #vitae::twentyseconds
 # docname: CV/Resume
#css:['css/styles.css']

site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
#library(pillar)
#require(rlang)
library(tibble)

```

```{css echo=FALSE}
# .columns{display:flex;}
# body{background-color:lightblue}
# h1{color:red;}  
# h2{color:forestgreen;}

```


   * Australian Permanent Resident


## Some fun facts about me

  * I just love the whole process of gathering and interpreting data from a variety of sources using wide rage of tools to help in leveraging on details to target  quality outcomes and visual experience.
  
  * For over ten years I have routinely taught dozens of mathematics,statistical computation and computer programming courses at **University level**
  
  * I have over 10 plus years of experience with **Data Analysis,Executive data visualization,Machine Learning using R language and Python**.
  
  * I  maintain high level of proficient in the use of over **400** essential packages and I have written more  than **20,000**  **lines of  codes** in R  across wide range of application domain data sets from science to  engineering,from health to socioeconomic as well as spatial analysis of data sets of settlements and boundaries .
 
 * I believe in  the power of great team,efficient teamwork,positive thinking,big dream, good habits,hard-work ,reviewing of outcomes and love in the heart in order to achieve institutional/organizational strategic goals in the short, medium and long term .

## Education

```{r echo=FALSE}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "HRD Candidate in the Analysis of Complex System Networks and Strategic Interraction", "2019-Present", " University of Sydney", "Australia",
  "Master of Computer Science", "2015", "University  of Lagos", "Nigeria",
  "Bachelor of Mathematics with Computer Science", "2006", "Federal University of technology ", "Nigeria"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Experience

```{r echo=FALSE}
tibble::tribble(
  ~Year, ~Type, ~Desc,
  "Technical", "R Python HTML Javascript PostgreSQL/MySQLObject-oriented design Design and implement database structures", "Over ten years of experience  in data analytics associated with teaching, research and academic publications",
  "Professional", "Effective communication, Team player,Strong problem solver,Good time management", "Over ten years of experience in Teaching, research and collaboration"
) %>% 
  brief_entries(
    glue::glue("Skill set in {Type}"),
    Year, 
    Desc
  )
```

## Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

